\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-05-05 sections/methods.tex
Change: Merge the tool tables in the methods section

  \subsection*{Denoising and Clustering (DC)}
  \vspace{-5mm}
  This module deals with processing the quality-controlled, trimmed 16S sequence data into \ac{otu} or \ac{esv} count tables.
  It consists of the following processes: denoising (or clustering) and chimera checking.
  The denoise/cluster process handles the conversion of the demultiplexed, trimmed sequences into \ac{otu} or \ac{esv} count tables (some methods, like closed reference and open reference clustering, perform clustering and taxonomy assignment in the same step).
  The chimera checking process handles the removal of chimeric sequences created during the \ac{pcr} step.
  The output of this module is a matrix of counts, that describes the number of reads of a particular \ac{otu} or \ac{esv} (rows of the matrix) present in each sample (columns of the matrix).
  The options currently available in the pipeline for denoising and clustering are: open reference clustering, closed reference clustering and de novo clustering methods from the vsearch plugin of \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019} and denoising methods from \ac{dada2} v1.14~\cite{Callahan2016} (from the \ac{dada2} R package) and Deblur v1.1.0~\cite{Amir2017} (from the deblur plugin of \ac{qiime2}).
  The quality filtering and chimera checking tools are derived from those used in \ac{qiime2} v2021.8.0 (uchime-denovo method) and \ac{dada2} (remove bimera method).
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:dc_tools}.

  \subsection*{Taxonomy Assignment (TA)}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
  In order to assign taxonomies to a particular sequence we need a taxonomy database and a query tool.
  The taxonomy database contains the collection of 16S sequences of micro-organisms of interest and the query tool allows one to compare a sequence of interest to all the sequences in the database to identify the best matches.
  Finally, a consensus method is used to identify the most probable match from the list of best matches.
  The pipeline incorporates \ac{gg} 13\_8~\cite{DeSantis2006}, SILVA 138~\cite{Quast2012} and the \ac{ncbi} (16S RefSeq as of Oct 2021)~\cite{Sayers2009} databases for taxonomy assignment.
  These databases were downloaded and built using the RESCRIPt qiime2 plugin~\cite{iiRESCRIPtReproducibleSequence2021}.
  The Naive Bayes classifier and the \ac{ncbi} blast used as the query tools in this study were from the \ac{qiime2} package and the parameters used were also the defaults in the package.
  The consensus algorithm used is the default method used by the classifiers in \ac{qiime2}.
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:ta_tools}.

  \subsection*{OTU and ESV Processing (OP)}
  \vspace{-5mm}
  This module deals with normalization, filtering, forking, grouping and applying transformations to the \ac{otu} or \ac{esv} counts matrix.
  Normalization of the count matrix involves converting the count matrix of read counts into a count matrix containing relative abundances.
  The module also supports rarefaction, which is a normalization technique used to overcome the bias that might arise due to variable sampling depth in different samples.
  This is performed either by sub-sampling or by normalization of the matrix to the lowest sampling depth~\cite{Weiss2015}.
  Although the pipeline supports rarefaction, these modules are turned off by default and the analyses reported in the paper do not normalize or rareify the counts matrices.
  However, most of the network inference methods perform normalization and other transformation operations on the counts matrix as a part of their workflow.
  Filtering, is performed to remove samples or features (\ac{otu}s or \ac{esv}s) from the count matrix that are sparse.
  By default, when the OP module is ``on'', the samples are filtered out if the total reads in a sample are less than 500 and features are filtered out if the abundance is less than 1\%, prevalence is less than 5\% and count sum across all the samples is less than 100.
  When the OP module is ``off'', the filtering is still performed but only to remove those features that are very low in presence.
  The parameters used are given in Table~\ref{tab:op_tools}.
  The forking operation splits the count matrix into multiple matrices based on sample metadata column.
  The group operation transforms the \ac{otu} or \ac{esv} count matrix into a taxonomic count matrix at the requested level by adding up counts that map to the same taxonomy.
  Finally, transformations are performed in order to correct for and overcome the compositional bias that is inherent in a counts matrix (in analyses peformed in the study these are handled by the network inference algorithm).
  All the modules in this step were implemented using functions from the \href{http://biom-format.org/}{biom-format} Python package~\cite{mcdonaldBiologicalObservationMatrix2012}.

  \subsection*{Network Inference (NI)}
  \vspace{-5mm}
  This module deals with the inference of co-occurrence associations from the processed \ac{otu} or \ac{esv} counts matrix.
  The input count matrices are collapsed to the Genus level (or any other required taxonomy level) using the group module at the OP step.
  These collapsed matrices are as used as input to the network inference methods to produce association matrices at the appropriate taxonomy level.
  These associations can be represented as a network, with nodes representing taxonomies of the micro-organisms and edges representing the associations between them.
  A null model is created by re-sampling and bootstrapping the counts matrix and recalculating the correlations/associations.
  These bootstrapped association matrices are used to calculate the significance of the inferred associations by calculating the p-values against this null model~\cite{Watts2018}.
  The pipeline includes 4 methods for pairwise correlation metrics, and 6 methods for direct association metrics (refer Table~\ref{tab:ni_tools}).
  The Brown's p-value merging method~\cite{brown_400_1975} is used for combining p-values from the pairwise correlations methods to obtain a consensus p-value, which can be used to filter for significance.
  In the final module of this step, the consensus algorithms are used to create the final consensus network using associations from all the network inference methods.
  The output of this step are co-occurrence association networks encoded in the JSON format (refer Supplementary section) and are also exportable to a variety of network formats like .gml.
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:ni_tools}.

>>>>

  \subsection*{Denoising and Clustering (DC)}
  \vspace{-5mm}
  This module deals with processing the quality-controlled, trimmed 16S sequence data into \ac{otu} or \ac{esv} count tables.
  It consists of the following processes: denoising (or clustering) and chimera checking.
  The denoise/cluster process handles the conversion of the demultiplexed, trimmed sequences into \ac{otu} or \ac{esv} count tables (some methods, like closed reference and open reference clustering, perform clustering and taxonomy assignment in the same step).
  The chimera checking process handles the removal of chimeric sequences created during the \ac{pcr} step.
  The output of this module is a matrix of counts, that describes the number of reads of a particular \ac{otu} or \ac{esv} (rows of the matrix) present in each sample (columns of the matrix).
  The options currently available in the pipeline for denoising and clustering are: open reference clustering, closed reference clustering and de novo clustering methods from the vsearch plugin of \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019} and denoising methods from \ac{dada2} v1.14~\cite{Callahan2016} (from the \ac{dada2} R package) and Deblur v1.1.0~\cite{Amir2017} (from the deblur plugin of \ac{qiime2}).
  The quality filtering and chimera checking tools are derived from those used in \ac{qiime2} v2021.8.0 (uchime-denovo method) and \ac{dada2} (remove bimera method).
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:micone_tools}.

  \subsection*{Taxonomy Assignment (TA)}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
  In order to assign taxonomies to a particular sequence we need a taxonomy database and a query tool.
  The taxonomy database contains the collection of 16S sequences of micro-organisms of interest and the query tool allows one to compare a sequence of interest to all the sequences in the database to identify the best matches.
  Finally, a consensus method is used to identify the most probable match from the list of best matches.
  The pipeline incorporates \ac{gg} 13\_8~\cite{DeSantis2006}, SILVA 138~\cite{Quast2012} and the \ac{ncbi} (16S RefSeq as of Oct 2021)~\cite{Sayers2009} databases for taxonomy assignment.
  These databases were downloaded and built using the RESCRIPt qiime2 plugin~\cite{iiRESCRIPtReproducibleSequence2021}.
  The Naive Bayes classifier and the \ac{ncbi} blast used as the query tools in this study were from the \ac{qiime2} package and the parameters used were also the defaults in the package.
  The consensus algorithm used is the default method used by the classifiers in \ac{qiime2}.
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:micone_tools}.

  \subsection*{OTU and ESV Processing (OP)}
  \vspace{-5mm}
  This module deals with normalization, filtering, forking, grouping and applying transformations to the \ac{otu} or \ac{esv} counts matrix.
  Normalization of the count matrix involves converting the count matrix of read counts into a count matrix containing relative abundances.
  The module also supports rarefaction, which is a normalization technique used to overcome the bias that might arise due to variable sampling depth in different samples.
  This is performed either by sub-sampling or by normalization of the matrix to the lowest sampling depth~\cite{Weiss2015}.
  Although the pipeline supports rarefaction, these modules are turned off by default and the analyses reported in the paper do not normalize or rareify the counts matrices.
  However, most of the network inference methods perform normalization and other transformation operations on the counts matrix as a part of their workflow.
  Filtering, is performed to remove samples or features (\ac{otu}s or \ac{esv}s) from the count matrix that are sparse.
  By default, when the OP module is ``on'', the samples are filtered out if the total reads in a sample are less than 500 and features are filtered out if the abundance is less than 1\%, prevalence is less than 5\% and count sum across all the samples is less than 100.
  When the OP module is ``off'', the filtering is still performed but only to remove those features that are very low in presence.
  The parameters used are given in Table~\ref{tab:micone_tools}.
  The forking operation splits the count matrix into multiple matrices based on sample metadata column.
  The group operation transforms the \ac{otu} or \ac{esv} count matrix into a taxonomic count matrix at the requested level by adding up counts that map to the same taxonomy.
  Finally, transformations are performed in order to correct for and overcome the compositional bias that is inherent in a counts matrix (in analyses peformed in the study these are handled by the network inference algorithm).
  All the modules in this step were implemented using functions from the \href{http://biom-format.org/}{biom-format} Python package~\cite{mcdonaldBiologicalObservationMatrix2012}.

  \subsection*{Network Inference (NI)}
  \vspace{-5mm}
  This module deals with the inference of co-occurrence associations from the processed \ac{otu} or \ac{esv} counts matrix.
  The input count matrices are collapsed to the Genus level (or any other required taxonomy level) using the group module at the OP step.
  These collapsed matrices are as used as input to the network inference methods to produce association matrices at the appropriate taxonomy level.
  These associations can be represented as a network, with nodes representing taxonomies of the micro-organisms and edges representing the associations between them.
  A null model is created by re-sampling and bootstrapping the counts matrix and recalculating the correlations/associations.
  These bootstrapped association matrices are used to calculate the significance of the inferred associations by calculating the p-values against this null model~\cite{Watts2018}.
  The pipeline includes 4 methods for pairwise correlation metrics, and 6 methods for direct association metrics (refer Table~\ref{tab:micone_tools}).
  The Brown's p-value merging method~\cite{brown_400_1975} is used for combining p-values from the pairwise correlations methods to obtain a consensus p-value, which can be used to filter for significance.
  In the final module of this step, the consensus algorithms are used to create the final consensus network using associations from all the network inference methods.
  The output of this step are co-occurrence association networks encoded in the JSON format (refer Supplementary section) and are also exportable to a variety of network formats like .gml.
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:micone_tools}.

### 2022-05-05 sections/supplementary.tex
Change: Supl figure font sizes
Change: Merge the tool tables in the methods section

    % TODO: Rerun this figure
    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s6.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The precision and sensitivity of the inferred networks on the NorTA synthetic interaction data with Pearson and Spearman added to the consensus.}
            The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
            The different consensus based methods used are: pvalue merging, scaled-sum (SS) and simple voting (SV) method.
            With the addition of Pearson and Spearman in the consensus calculation we observe a decrease in the average precision scores of both the consensus algorithms.
            The overall best precision was still consistently obtained by the scaled-sum method (0.985, 0.963 and 1.000), but the performance was not stable to changes in parameter value.
            The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), again outperforms \ac{spieceasi} on average precision (0.961).
        }
      \label{fig:figure_s6}
    \end{figure}
    \FloatBarrier
    \newpage

@@

    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s7.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The precision and sensitivity of the inferred networks on the seqtime synthetic interaction data.}
          The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
          The different consensus based methods used are: pvalue merging, scaled-sum (SS) and simple voting (SV) method.
          Pearson and Spearman methods are not used in the calculation of the consensus.
          Among all the independent network inference methods, \ac{spieceasi} has the best average precision (0.624), but the overall best precision was consistently obtained by the scaled-sum method (0.688, 0.820 and 1.000).
          The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), also outperforms \ac{spieceasi} on average precision (0.692).
        }
      \label{fig:figure_s7}
    \end{figure}
    \FloatBarrier
    \newpage

@@

    The default format \ac{micone} uses for storing the network files is the JSON format.
    The custom JSON schema we have designed is able to store all network related information from nodes and links to metadata related to links and datasets.
    Additionally, \ac{micone} also supports exporting of networks into a variety of other formats such as edge lists, .gml and cytoscape formats.
    Since, we make use of \texttt{networkx}~\cite{hagbergExploringNetworkStructure2008} for the export functionality, networks can be exported to all supported formats but the corresponding metadata might not be exported appropriately.
    The details of the format and information about importing/exporting it and other network formats can be found in the \ac{micone} documentation.

>>>>

    % TODO: Rerun this figure
    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s6.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The precision and sensitivity of the inferred networks on the NorTA synthetic interaction data with Pearson and Spearman added to the consensus.}
            The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
            The different consensus based methods used are: pvalue merging (PM), scaled-sum (SS) and simple voting (SV) method.
            With the addition of Pearson and Spearman in the consensus calculation we observe a decrease in the average precision scores of both the consensus algorithms.
            The overall best precision was still consistently obtained by the scaled-sum method (0.985, 0.963 and 1.000), but the performance was not stable to changes in parameter value.
            The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), again outperforms \ac{spieceasi} on average precision (0.961).
        }
      \label{fig:figure_s6}
    \end{figure}
    \FloatBarrier
    \newpage

@@

    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s7.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The precision and sensitivity of the inferred networks on the seqtime synthetic interaction data.}
          The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
          The different consensus based methods used are: pvalue merging (PM), scaled-sum (SS) and simple voting (SV) method.
          Pearson and Spearman methods are not used in the calculation of the consensus.
          Among all the independent network inference methods, \ac{spieceasi} has the best average precision (0.624), but the overall best precision was consistently obtained by the scaled-sum method (0.688, 0.820 and 1.000).
          The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), also outperforms \ac{spieceasi} on average precision (0.692).
        }
      \label{fig:figure_s7}
    \end{figure}
    \FloatBarrier
    \newpage

@@

    The default format \ac{micone} uses for storing the network files is the JSON (JavaScript Object Notation) format.
    The custom JSON schema we have designed is able to store all network related information from nodes and links to metadata related to links and datasets.
    Additionally, \ac{micone} also supports exporting of networks into a variety of other formats such as edge lists, .gml and cytoscape formats.
    Since, we make use of \texttt{networkx}~\cite{hagbergExploringNetworkStructure2008} for the export functionality, networks can be exported to all supported formats but the corresponding metadata might not be exported appropriately.
    The details of the format and information about importing/exporting it and other network formats can be found in the \ac{micone} documentation.

### 2022-05-05 sections/tables_figures.tex
Change: Update font size and scaling of main figures
Change: Supl figure font sizes
Change: Merge the tool tables in the methods section

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Process} & \textbf{Tool} \\
      \hline
      Denoising and Clustering & Dada2 and remove bimera \\
      Taxonomy Assignment & \ac{gg} with NaiveBayes classifier \\
      OTU Processing & Thresholds on prevalence and abundance \\
      Network Inference & scaled-sum consensus method \\
      \hline
    \end{tabular}
    \caption{Default tools and parameters for the pipeline}
    \label{tab:default_options}
  \end{table}

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Module} & \textbf{Tool} & \textbf{References} \\
      \hline
      Denoising and Clustering & Closed reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Denoising and Clustering & Open reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Denoising and Clustering & De novo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Denoising and Clustering & Dada2 & \cite{Callahan2016} \\
      Denoising and Clustering & Deblur & \cite{Amir2017,bolyenReproducibleInteractiveScalable2019} \\
      \hline
      Chimera checking & Uchime-denovo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Chimera checking & Remove bimera & \cite{Callahan2016} \\
      \hline
    \end{tabular}
    \caption{Tools used in the DC module}
    \label{tab:dc_tools}
  \end{table}

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Module} & \textbf{Tool/Database} & \textbf{References} \\
      \hline
      Query tool & Blast & \cite{camachoBLASTArchitectureApplications2009,bokulichOptimizingTaxonomicClassification2018} \\
      Query tool & Naive bayes classifier & \cite{bokulichOptimizingTaxonomicClassification2018} \\
      \hline
      Database & Greengenes & \cite{DeSantis2006} \\
      Database & SILVA & \cite{Quast2012} \\
      Database & NCBI RefSeq & \cite{Sayers2009} \\
      \hline
    \end{tabular}
    \caption{Tools used in the TA module}
    \label{tab:ta_tools}
  \end{table}

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
    \hline
    Condition                    & Parameter                 & Value          \\ \hline
    \multirow{3}{*}{Filter(off)} & Prevalence threshold      & 2 / n\_samples \\ \cline{2-3}
                                 & Abundance threshold       & 0.001          \\ \cline{2-3}
                                 & Observation sum threshold & 10             \\ \hline
    \multirow{3}{*}{Filter(on)}  & Prevalence threshold      & 0.05           \\ \cline{2-3}
                                 & Abundance threshold       & 0.01           \\ \cline{2-3}
                                 & Observation sum threshold & 100            \\ \hline
    \end{tabular}
    \caption{Parameters used in the OP module}
    \label{tab:ni_tools}
  \end{table}

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Module} & \textbf{Tool/Database} & \textbf{References} \\
      \hline
      Booststrap & \texttt{fastspar\_bootstraps} v1.0 & \cite{Watts2018} \\
      Booststrap & \texttt{fastspar\_pvalues} v1.0 & \cite{Watts2018} \\
      \hline
      Direct & \ac{spieceasi} v1.1.2 & \cite{Kurtz2015} \\
      Direct & FlashWeave.jl v0.18.1 & \cite{tackmannRapidInferenceDirect2019} \\
      Direct & \ac{cozine} v1.0 & \cite{haCompositionalZeroinflatedNetwork2020a} \\
      Direct & \ac{harmonies} v1.0 & \cite{jiangHARMONIESHybridApproach2020} \\
      Direct & \ac{spring} v1.0.4 & \cite{yoonMicrobialNetworksSPRING2019} \\
      Direct & \ac{mldm} v1.1 & \cite{Yang2017} \\
      \hline
      Correlation & FastSpar (\ac{sparcc}) v1.0 & \cite{Watts2018} \\
      Correlation & Pearson & - \\
      Correlation & Spearman & - \\
      Correlation & propr v2.1.2 & \cite{quinnProprRpackageIdentifying2017} \\
      \hline
    \end{tabular}
    \caption{Tools used in the NI module}
    \label{tab:ni_tools}
  \end{table}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.75\linewidth]{figure1.pdf}
  \end{figure}
  \begin{figure}[ht!]
    \centering
    \caption{
      \textbf{The workflow of the \ac{micone} pipeline}.
      The steps can be grouped into five major groups: \textbf{(SP)} \textbf{S}equence \textbf{P}rocessig, \textbf{(DC)} \textbf{D}enoising and \textbf{C}lustering, \textbf{(TA)} \textbf{T}axonomy \textbf{A}ssignment, \textbf{(OP)} \textbf{O}TU or ESV \textbf{P}rocessing, and \textbf{(NI)} \textbf{N}etwork \textbf{I}nference.
      Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
      The text along the arrows describes the data that is being passed from one step to another.
      The final output of the pipeline are consensus networks generated from the co-occurrence networks.
      For details on each process and data types, see Methods.
    }
    \label{fig:figure1}
  \end{figure}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=1.0\linewidth]{figure6.pdf}
    \caption{
      \textbf{The precision and sensitivity of the inferred networks on the NorTA synthetic interaction data.}
      The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
      The different consensus based methods used are: pvalue merging, scaled-sum (SS) and simple voting (SV) method.
      Pearson and Spearman methods are not used in the calculation of the consensus.
      Among all the independent network inference methods, \ac{spieceasi} has the best average precision (0.944), but the overall best precision was consistently obtained by the scaled-sum method (0.956, 0.985 and 1.000).
      The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), also outperforms \ac{spieceasi} on average precision (0.969).
      Therefore, we recommend the scaled-sum consensus method as the default tool for network inference.
    }
    \label{fig:figure6}
  \end{figure}
  \FloatBarrier
  \newpage

>>>>

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|c|}
      \hline
      \textbf{Workflow step} & \textbf{Module/Condition} & \textbf{Tool/Parameter} & \textbf{References/Value} \\
      \hline
      \multirow{7}{*}{Denoising and Clustering} & \multirow{5}{*}{Denoising and Clustering} & Closed reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                &  & Open reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                &  & De novo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                &  & Dada2 & \cite{Callahan2016} \\
                                                &  & Deblur & \cite{Amir2017,bolyenReproducibleInteractiveScalable2019} \\
                                                \cline{2-4}
                                                & \multirow{2}{*}{Chimera checking} & Uchime-denovo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
                                                & & Remove bimera & \cite{Callahan2016} \\
                                                \hline
      \multirow{5}{*}{Taxonomy assignment} &  \multirow{2}{*}{Query tool} & Blast & \cite{camachoBLASTArchitectureApplications2009,bokulichOptimizingTaxonomicClassification2018} \\
                                           &  & Naive bayes classifier & \cite{bokulichOptimizingTaxonomicClassification2018} \\
                                           \cline{2-4}
                                           & \multirow{3}{*}{Database} & Greengenes & \cite{DeSantis2006} \\
                                           & & SILVA & \cite{Quast2012} \\
                                           & & NCBI RefSeq & \cite{Sayers2009} \\
      \hline
      \multirow{6}{*}{OTU processing} & \multirow{3}{*}{Filter(off)} & Prevalence threshold      & 2 / n\_samples \\
                                      & & Abundance threshold       & 0.001          \\
                                      & & Observation sum threshold & 10             \\ \cline{2-4}
                                      & \multirow{3}{*}{Filter(on)}  & Prevalence threshold      & 0.05           \\
                                      & & Abundance threshold       & 0.01           \\
                                      & & Observation sum threshold & 100            \\
      \hline
      \multirow{12}{*}{Network Inference} & \multirow{2}{*}{Bootstrapping}& \texttt{fastspar\_bootstraps} v1.0 & \cite{Watts2018} \\
                                          & & \texttt{fastspar\_pvalues} v1.0 & \cite{Watts2018} \\
                                          \cline{2-4}
                                          & \multirow{6}{*}{Direct association} & \ac{spieceasi} v1.1.2 & \cite{Kurtz2015} \\
                                          & & FlashWeave.jl v0.18.1 & \cite{tackmannRapidInferenceDirect2019} \\
                                          & & \ac{cozine} v1.0 & \cite{haCompositionalZeroinflatedNetwork2020a} \\
                                          & & \ac{harmonies} v1.0 & \cite{jiangHARMONIESHybridApproach2020} \\
                                          & & \ac{spring} v1.0.4 & \cite{yoonMicrobialNetworksSPRING2019} \\
                                          & & \ac{mldm} v1.1 & \cite{Yang2017} \\
                                          \cline{2-4}
                                          & \multirow{2}{*}{Correlation-based} & FastSpar (\ac{sparcc}) v1.0 & \cite{Watts2018} \\
                                          & & Pearson & - \\
                                          & & Spearman & - \\
                                          & & propr v2.1.2 & \cite{quinnProprRpackageIdentifying2017} \\
      \hline
    \end{tabular}
    \caption{Tools used in the \ac{micone} pipeline}
    \label{tab:micone_tools}
  \end{table}

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Workflow step} & \textbf{Default tool} \\
      \hline
      Denoising and Clustering & Dada2 and remove bimera \\
      Taxonomy Assignment & \ac{gg} with NaiveBayes classifier \\
      OTU Processing & Thresholds on prevalence and abundance \\
      Network Inference & scaled-sum consensus method \\
      \hline
    \end{tabular}
    \caption{Default tools and parameters of the \ac{micone} pipeline}
    \label{tab:default_options}
  \end{table}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.74\linewidth]{figure1.pdf}
  \end{figure}
  \begin{figure}[ht!]
    \centering
    \caption{
      \textbf{The workflow of the \ac{micone} pipeline}.
      The steps can be grouped into five major groups: \textbf{(SP)} \textbf{S}equence \textbf{P}rocessig, \textbf{(DC)} \textbf{D}enoising and \textbf{C}lustering, \textbf{(TA)} \textbf{T}axonomy \textbf{A}ssignment, \textbf{(OP)} \textbf{O}TU or ESV \textbf{P}rocessing, and \textbf{(NI)} \textbf{N}etwork \textbf{I}nference.
      Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
      The text along the arrows describes the data that is being passed from one step to another.
      The final output of the pipeline are consensus networks generated from the co-occurrence networks.
      For details on each process and data types, see Methods.
    }
    \label{fig:figure1}
  \end{figure}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=1.0\linewidth]{figure6.pdf}
    \caption{
      \textbf{The precision and sensitivity of the inferred networks on the NorTA synthetic interaction data.}
      The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
      The different consensus based methods used are: pvalue merging (PM), scaled-sum (SS) and simple voting (SV) method.
      Pearson and Spearman methods are not used in the calculation of the consensus.
      Among all the independent network inference methods, \ac{spieceasi} has the best average precision (0.944), but the overall best precision was consistently obtained by the scaled-sum method (0.956, 0.985 and 1.000).
      The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), also outperforms \ac{spieceasi} on average precision (0.969).
      Therefore, we recommend the scaled-sum consensus method as the default tool for network inference.
    }
    \label{fig:figure6}
  \end{figure}
  \FloatBarrier
  \newpage
